---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# brilliant

<!-- badges: start -->
<!-- badges: end -->

The goal of brilliant is to ...

## Installation

You can install the development version of this package from [GitHub](https://github.com/), if you have `devtools` installed, using:

``` r
# install.packages("devtools")
devtools::install_github("chrismainey/brilliant")
```
## Example

This is a demo package for UCL IHI code club.  We built a package with a single function for calculating a percentage.  We used `roxygen2` to build the NAMESPACE, document the functions, building the help files.  We also added a basic unit test using the `testthat` package, and an AGPL-3 licence using functions from the `usethis` package.  `usethis` is a great tool for helping with all sorts of development tasks.

```{r example}
library(brilliant)

percentage(20,50)

```


